Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-08-05 Supplemental-Material-A-Annotated-Analysis.Rmd
s1VarOut added for MI

MiMain <-
  amelia(
    dtMiMain,
    m = 1, # 20
    ts = "TIDnum",
    cs = "ID",
    idvars = c("TID", "date", "week", "study"), #"PID",
    #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
    #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
    #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
    parallel = "multicore",
    ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiMain, file = "data/imputed/MainImputed.RData")
load("data/imputed/MainImputed.RData")

MiMainDaily <-
  amelia(
    dtMiMainDaily,
    m = 1, # 20
    ts = "TIDnum",
    cs = "ID",
    idvars = c("date", "study"), #"PID",
    #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
    #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
    #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
    parallel = "multicore",
    ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiMainDaily, file = "data/imputed/MainDailyImputed.RData")
load("data/imputed/MainDailyImputed.RData")

MiMainWeekly <-
  amelia(
    dtMiMainWeeekly,
    m = 1, # 20
    ts = "TIDnum",
    cs = "ID",
    idvars = c("week", "study"), #"PID",
    #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
    #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
    #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
    parallel = "multicore",
    ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiMainWeekly, file = "data/imputed/MainWeeklyImputed.RData")
load("data/imputed/MainWeeklyImputed.RData")
```

@@

dtMiS1 <- dtMiS1 %>%
  mutate(
    assimilation.dif = assimilation.post - assimilation.pre,
    integration.dif = integration.post - integration.pre,
    marginalization.dif = marginalization.post - marginalization.pre,
    separation.dif = separation.post - separation.pre,
    VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
    VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
    IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
    swl.dif = swl.post_calc - swl.pre_calc
  ) %>% 
  select(
    -any_of(varNamDifS1)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

dtMiS1Daily <- dtMiS1Daily %>%
  mutate(
    assimilation.dif = assimilation.post - assimilation.pre,
    integration.dif = integration.post - integration.pre,
    marginalization.dif = marginalization.post - marginalization.pre,
    separation.dif = separation.post - separation.pre,
    VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
    VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
    IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
    swl.dif = swl.post_calc - swl.pre_calc
  ) %>% 
  select(
    -any_of(varNamDifS1)
  ) %>%
  select(PID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

dtMiS1Weekly <- dtMiS1Weekly %>%
  mutate(
    assimilation.dif = assimilation.post - assimilation.pre,
    integration.dif = integration.post - integration.pre,
    marginalization.dif = marginalization.post - marginalization.pre,
    separation.dif = separation.post - separation.pre,
    VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
    VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
    IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
    swl.dif = swl.post_calc - swl.pre_calc
  ) %>% 
  select(
    -any_of(varNamDifS1)
  ) %>%
  select(PID,
         TIDnum,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

@@

@@

# MiS1 <-
#   amelia(
#     dtMiS1,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("TID", "date", "week"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1, file = "data/imputed/S1Imputed.RData")
# load("data/imputed/S1Imputed.RData")
# 
# MiS1Daily <-
#   amelia(
#     dtMiS1Daily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("date", "week"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 2
#   )
# save(MiS1Daily, file = "data/imputed/S1DailyImputed.RData")
# load("data/imputed/S1DailyImputed.RData")
# 
# MiS1Weekly <-
#   amelia(
#     dtMiS1Weekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "PID",
#     idvars = c("week"),
#     # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
#     # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
#     # leads = ...,
#     # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
#     # parallel = "multicore",
#     # ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiS1Weekly, file = "data/imputed/S1WeeklyImputed.RData")
# load("data/imputed/S1WeeklyImputed.RData")
```

>>>>

# MiMain <-
#   amelia(
#     dtMiMain,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("TID", "date", "week", "study"), #"PID",
#     #lags = names(dtMiMain)[!names(dtMiMain) %in% idVars],
#     #lags = names(dtMiMain)[names(dtMiMain) %in%varNamInMiMainRed],
#     #noms = names(dtMiMain)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMain))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMain, file = "data/imputed/MainImputed.RData")
load("data/imputed/MainImputed.RData")

# MiMainDaily <-
#   amelia(
#     dtMiMainDaily,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("date", "study"), #"PID",
#     #lags = names(dtMiMainDaily)[!names(dtMiMainDaily) %in% idVars],
#     #lags = names(dtMiMainDaily)[names(dtMiMainDaily) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainDaily)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainDaily))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainDaily, file = "data/imputed/MainDailyImputed.RData")
load("data/imputed/MainDailyImputed.RData")

# MiMainWeekly <-
#   amelia(
#     dtMiMainWeeekly,
#     m = 1, # 20
#     ts = "TIDnum",
#     cs = "ID",
#     idvars = c("week", "study"), #"PID",
#     #lags = names(dtMiMainWeeekly)[!names(dtMiMainWeeekly) %in% idVars],
#     #lags = names(dtMiMainWeeekly)[names(dtMiMainWeeekly) %in%varNamInMiMainRed],
#     #noms = names(dtMiMainWeeekly)[grepl(paste(varNamMiMainNoms, collapse = "|^"), names(dtMiMainWeeekly))],
#     parallel = "multicore",
#     ncpus = parallel::detectCores(),
#     p2s = 1
#   )
# save(MiMainWeekly, file = "data/imputed/MainWeeklyImputed.RData")
load("data/imputed/MainWeeklyImputed.RData")
```

@@

# Variables removed for study 1 due to high multicollinearity:
varNamS1Out <- dtMiS1 %>%
  select(
    any_of(varNamDifS1),
    mdmq.calmness.pre_calc,
    mdmq.alertness.pre_calc,
    mdmq.valence.pre_calc,
    relatednessFrust.pre_calc,
    competenceFrust.pre_calc,
    competenceSat.pre_calc,
    relatednessSat.pre_calc,
    DutchFriends.pre,
    secNatDum.pre,
    timeNL.pre,
    stress.post,
    discrimination_month.post,
    rosenberg.post,
    qualityStar,
    starts_with("SSAS")
  ) %>%
  names

dtMiS1 <- dtMiS1 %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out)
  ) %>%
  select(PID,
         TID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

dtMiS1Daily <- dtMiS1Daily %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out)
  ) %>%
  select(PID,
         TIDnum,
         date,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

dtMiS1Weekly <- dtMiS1Weekly %>%
  # mutate(
  #   assimilation.dif = assimilation.post - assimilation.pre,
  #   integration.dif = integration.post - integration.pre,
  #   marginalization.dif = marginalization.post - marginalization.pre,
  #   separation.dif = separation.post - separation.pre,
  #   VIA_Dutch.dif = VIA_Dutch.post - VIA_Dutch.post,
  #   VIA_heritage.dif = VIA_heritage.post - VIA_heritage.pre,
  #   IntGrAnx.dif = IntGrAnx.post_calc - IntGrAnx.pre_calc,
  #   swl.dif = swl.post_calc - swl.pre_calc
  # ) %>% 
  select(
    -any_of(varNamS1Out)
  ) %>%
  select(PID,
         TIDnum,
         week,
         which(sapply(., sd, na.rm = TRUE) > 0)) %>%
  as.data.frame

@@

lares::corr_cross(
  dtMiS1Daily %>% select_if(is.numeric), # name of dataset
  max_pvalue = 0.05, # display only significant correlations (at 5% level)
  top = 20 # display top 20 couples of variables (by correlation coefficient)
)

@@

MiS1 <-
  amelia(
    dtMiS1,
    m = 1, # 20
    ts = "TIDnum",
    cs = "PID",
    idvars = c("TID", "date", "week"),
    # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
    # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
    # leads = ...,
    # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
    # parallel = "multicore",
    # ncpus = parallel::detectCores(),
    p2s = 2
  )
save(MiS1, file = "data/imputed/S1Imputed.RData")
load("data/imputed/S1Imputed.RData")

MiS1Daily <-
  amelia(
    dtMiS1Daily,
    m = 1, # 20
    ts = "TIDnum",
    cs = "PID",
    idvars = c("date", "week"),
    # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
    # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
    # leads = ...,
    # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
    # parallel = "multicore",
    # ncpus = parallel::detectCores(),
    p2s = 2
  )
save(MiS1Daily, file = "data/imputed/S1DailyImputed.RData")
load("data/imputed/S1DailyImputed.RData")

MiS1Weekly <-
  amelia(
    dtMiS1Weekly,
    m = 1, # 20
    ts = "TIDnum",
    cs = "PID",
    idvars = c("week"),
    # lags = names(dtMiS1)[!names(dtMiS1) %in% idVars],
    # lags = names(dtMiS1)[names(dtMiS1) %in% varNamS1MiPsbl], # alternative?
    # leads = ...,
    # noms = names(dtMiS1)[grepl(paste(varNamdtS1Noms, collapse = "|^"), names(dtMiS1))],
    # parallel = "multicore",
    # ncpus = parallel::detectCores(),
    p2s = 1
  )
save(MiS1Weekly, file = "data/imputed/S1WeeklyImputed.RData")
load("data/imputed/S1WeeklyImputed.RData")
```
